Experiment 3 of 4

### 2017-05-15 experiments/e3/writeup/e3.Rmd
revisited May 2017; the only changes I have made are to get the original code to run

---
title: "Experiment 3 of 4"
author: "Matt Green"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    <!--code_folding: show-->
    theme: default
---  
<style>
table, th, td {
    border: 1px grey;
    border-collapse: collapse;
    padding:2px 5px 2px 5px
}  
</style>

@@

```{r trimat25sd}
trimdata <- perSubjectTrim.fnc(rawdata, response='RT', subject='Subject', trim = 2.5)$data
rtdata <- trimdata
```
```{r computeSummariesForGraphs, cache=TRUE, message=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, measurevar="RT_log", withinvars=c("Condition", "Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r rtplot, fig.width=7, fig.height=3, echo=F}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=' ', rtdataplot1$Selection, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
rtplot
```

>>>>

---
title: "Experiment 3 of 4"
author: "Matt Green"
output:
  html_document:
    toc: true
    <!--toc_float: true-->
    mathjax: default
    template: default
    code_folding: show
    theme: default
---  
<style>
table, th, td {
    border: 1px grey;
    border-collapse: collapse;
    padding:2px 5px 2px 5px
}  
</style>

@@

```{r trimat25sd}
trimdata <- perSubjectTrim.fnc(rawdata, response='RT', subject='Subject', trim = 2.5)$data
rtdata <- trimdata
```

```{r computeSummariesForGraphs, cache=TRUE, message=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r rtplot, fig.width=7, fig.height=3}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=' ', rtdataplot1$Selection, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
rtplot
```
